The Linear Instability of Dilute Ultrarelativistic \epm\ Pair Beams

### 2016-09-21 apjRevised/response.txt

REVIEWER:

2) Claiming that most of the kinetic energy of the pairs is dissipated into electrostatic turbulence on the ground, that the minimum linear instability groth time is shorter
than the inverse Compton energy loss time, is insufficient and not correct. The backreaction of the electrostatic turbulence on the unstable pair distribution function will ultimately lead to a plateaued distribution function in the original beam direction (see Menzler and Schlickeiser 2015, MNRAS 448, 3405) on a time scale much longer than the minimum linear growth time. The pairs are so redistributed in energy but still able to inverse Compton scatter the CMB photons. The authors should address this redistribution time scale and compare it with the inverse Compton energy loss time scale.

RESPONSE:

We completely agree with the referee that this statement is not correct and while we do not make this claim in this paper, we can understand how the discussion in the introduction can give this impression.  We were aware of these subtleties and focus just on the linear physics in this paper avoid any quantitative comparison with the ICC timescales.  We merely confirmed the linear results used in earlier papers, clarified the physics, especially in regard to the broad support of modes that are unstable, and address the transition between the kinetic and reactive mode for the oblique instability.

### 2016-09-21 apjRevised/ms.tex
small edits

\begin{abstract}
The annihilation of TeV photons from extragalactic TeV sources and the extragalactic background light produces ultrarelativistic $\epm$ beams, which are subject to powerful plasma instabilities that sap their kinetic energy.
Here we  study {\bf \sout{the initial conditions of these e± beams and}} the linear phase of the plasma instabilities that these pair beams drive.  Here we calculate the linear growth rate of the beam plasma and oblique instability in the electrostatic approximation in both the reactive and kinetic regimes{\bf,  assuming a Maxwell-J{\"u}ttner distribution for the pair beam}.  We reproduce the well-known reactive and kinetic growth rates for both the beam plasma and oblique mode. We demonstrate for the oblique instability that there is broad spectrum of unstable modes that grow at the maximum rate for a wide range of beam temperatures and wavevector orientations relative to the beam.  We also delineate the conditions for applicability for the reactive and kinetic regimes and find that the beam plasma mode transitions to the reactive regime at a lower Lorentz factor than the oblique mode due to a combination of their different scalings and the anisotropy of the velocity dispersions.  Applying these results to the ultrarelativistic $\epm$ beams from TeV blazars, we confirm that these beams are unstable to the both the kinetic oblique mode and the reactive beam-plasma mode.  These results are important in understanding how powerful plasma instabilities may sap the energy of the ultrarelativistic $\epm$ beams as they propagate through intergalactic space.
\end{abstract}

@@

These two important conclusions depend on IC cooling dominating the evolution of the ultra-relativistic pairs.  However, it was recently found that plasma instabilities driven by the
ultrarelativistic pair beams  likely are the dominant cooling mechanisms
(\citealt{paperI}, hereafter BCP12, \citealt{Schlickeiser+12,Schlickeiser+13}), depositing this energy
as heat in the intergalactic medium \citep{paperII,paperIII}.  Therefore, the lack of an observed
 IC halo emission from TeV blazars does not imply the existence of the IGMF as previous groups have argued
(BCP12;\citealt{Schlickeiser+12,Schlickeiser+13}). {\bf We note that this effectiveness of this plasma instabilities is complicated by nonlinear effects, which we briefly discuss below.}

>>>>

\begin{abstract}
The annihilation of TeV photons from extragalactic TeV sources and the extragalactic background light produces ultrarelativistic $\epm$ beams, which are subject to powerful plasma instabilities that sap their kinetic energy.
Here we  study {\bf \sout{the initial conditions of these e± beams and}} the linear phase of the plasma instabilities that these pair beams drive.  {\bf \sout{Here} To this end,} we calculate the linear growth rate of the beam plasma and oblique instability in the electrostatic approximation in both the reactive and kinetic regimes{\bf,  assuming a Maxwell-J{\"u}ttner distribution for the pair beam}.  We reproduce the well-known reactive and kinetic growth rates for both the beam plasma and oblique mode. We demonstrate for the oblique instability that there is a broad spectrum of unstable modes that grow at the maximum rate for a wide range of beam temperatures and wave vector orientations relative to the beam.  We also delineate the conditions for applicability for the reactive and kinetic regimes and find that the beam plasma mode transitions to the reactive regime at a lower Lorentz factor than the oblique mode due to a combination of their different scalings and the anisotropy of the velocity dispersions.  Applying these results to the ultrarelativistic $\epm$ beams from TeV blazars, we confirm that these beams are unstable to both, the kinetic oblique mode and the reactive beam-plasma mode.  These results are important in understanding how powerful plasma instabilities may sap the energy of the ultrarelativistic $\epm$ beams as they propagate through intergalactic space.
\end{abstract}

@@

These two important conclusions depend on IC cooling dominating the evolution of the ultra-relativistic pairs.  However, it was recently found that plasma instabilities driven by the
ultrarelativistic pair beams  likely are the dominant cooling mechanisms
(\citealt{paperI}, hereafter BCP12, \citealt{Schlickeiser+12,Schlickeiser+13}), depositing this energy
as heat in the intergalactic medium \citep{paperII,paperIII}.  Therefore, the lack of an observed
 IC halo emission from TeV blazars does not imply the existence of the IGMF as previous groups have argued
(BCP12;\citealt{Schlickeiser+12,Schlickeiser+13}). {\bf We note that the effectiveness of these plasma instabilities is complicated by nonlinear effects, which we briefly discuss below.}
